Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-02-18 Paper/Manuscript.tex

Based on the point scattering strength samples and the phase angle samples, single targets can be detected, and range and bearing to the single targets can be estimated. This is typically achieved through a single echo detection algorithm (SED). Here we will assume that the samples from the pulse compressed data $\ypc(\samplesymt)$ originating from single target already have been identified, noting that the number of samples after the detected target may be higher than those those before the peak to include scattering processes for beyond ideal point targets. The alongship angle $\along_n$, athwartship angle $\athw_n$ and range $r_n$ at the \emph{peak} $\ypc(\samplesymt)$ (or peak $S_p(n)$?? current code uses $\ypc$) is used as estimates for $\along_t$, $\athw_t$ and $r_t$, respectively. A simple pseudo SED algorithm is implemented in the code for illustrative purposes.
%
\begin{figure}
%\includegraphics[width=\reprintcolumnwidth]{'Fig_SED'}
\caption{\label{fi:SED}Illustrate the single target data somehow.}
\end{figure}

@@

Target strength can then be estimated using Eq. \ref{eq:TS}, but with $\freqsym$ replaced by the discrete index of frequency, $\samplesymf$:
\begin{equation}
\label{eq:TS_f}
\ts(\samplesymf) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range) + 2\absorp(\samplesymf)\range 
- 10\log_{10}\left( \frac{\ptxe \wlen_\samplesymf^2 \gain^2(\along,\athw,\samplesymf)}{16\pi^2} \right).
\end{equation}

>>>>

Lars: The peak in the send pulse needs to match with the peak in the signal.

Based on the point scattering strength samples and the phase angle samples, single targets can be detected, and range and bearing to the single targets can be estimated. This is typically achieved through a single echo detection algorithm (SED). Here we will assume that the samples from the pulse compressed data $\ypc(\samplesymt)$ originating from single target already have been identified, noting that the number of samples after the detected target may be higher than those those before the peak to include scattering processes for beyond ideal point targets. The alongship angle $\along_n$, athwartship angle $\athw_n$ and range $r_n$ at the \emph{peak} $\ypc(\samplesymt)$ (or peak $S_p(n)$?? current code uses $\ypc$) is used as estimates for $\along_t$, $\athw_t$ and $r_t$, respectively. A simple pseudo SED algorithm is implemented in the code for illustrative purposes.
%
\begin{figure}
\includegraphics[width=16cm]{Fig_singleTarget}
\caption{\label{fi:SED} The power (upper) and split beam angles (lower) for the single target. The vertical line corresponds to the range and angles for the single target.}
\end{figure}

@@

Target strength can then be estimated using Eq. \ref{eq:TS}, but with $\freqsym$ replaced by the discrete index of frequency, $\samplesymf$:
\begin{equation}
\label{eq:TS_f}
\ts(\samplesymf) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range_t) + 2\absorp(\samplesymf)\range_t 
- 10\log_{10}\left( \frac{\ptxe \wlen_\samplesymf^2 \gain^2(\along_t,\athw_t,f_\samplesymf)}{16\pi^2} \right).
\end{equation}

Usikker på om vi skal bruka indeksar eller variablar for gain.
